\documentclass[11pt]{article}

\usepackage{titlesec}
\usepackage{multicol}
\usepackage{titling}
\usepackage{color}
\usepackage{xcolor}
\usepackage[document]{ragged2e}
\usepackage[margin=.2in]{geometry}


\pagenumbering{gobble}
\clearpage

\titleformat{\section}
{\huge }
{}
{1em}
{ \bfseries }[\titlerule]

\titleformat{\subsection}[runin]
{\bfseries }
{\hspace{-.1in}}
{0em}
{}[\hfill]

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{-1em}
{}[::]

\titlespacing{\subsubsection}
{2em} %Pre-spacing Horizontal
{1em} %Pre-Spacing Vertical
{0em} %Post-Spacing Vertical

\renewcommand{\maketitle}{
\begin{multicols}{2}
\begin{flushleft}
   {\huge \bfseries
   \theauthor\\}
   {\color{red} Software Engineer}
\end{flushleft}

\columnbreak

\begin{flushright}
{\bfseries ZacharyOwen@acm.org} \\
www.github.com/zaowen \\
zaowen.github.io \\
\end{flushright}
\end{multicols}
}
\author{Zachary Owen}

\begin{document}

\maketitle

\section{E{\color{gray}xperience}}

\subsection{Black Hills Engineering Development Center: 3D Generalist \hfill}
{\it May 2019 - Current}
\begin{itemize}
\setlength\itemsep{-.5em}
\item Created safety, commecial and training experiences for Oculus, Microsoft Hololens and SteamVR platforms
\item Created Bezier based mesh generation and toolsets.
\end{itemize}

\subsection{Black Hills Information Security \hfill}
{\it May 2017 - Aug '18}
\begin{itemize}
\setlength\itemsep{-.5em}
\item Created a plugin that outputs connection logs created by the Bro IDS packet analyzer to MongoDB. 
\item Created documentation for Bro-Plugins.
\end{itemize}

\subsection{Sencore: Software Engineering Internship \hfill}
{\it May 2017 - Aug '17}
\begin{itemize}
\setlength\itemsep{-.5em}
\item Attained experience with Git/SVN source control as well as CI with crucible and gerrit.
\item Created program for configuring proprietary video over IP machines on device and over ssh.
\end{itemize}

\iffalse
\subsection{SDSMT Mechanical Engineering Dept \hfill}
{\it Sept 2014 - Nov '14}
\begin{itemize}
\setlength\itemsep{-.5em}
\item Ported a FORTRAN77 engine piston simulation program to the more recent Fujitsu compiler. 
\item Created front end display and management program for engine piston simulation in C\#
\end{itemize}
\fi

\section{P{\color{gray}rojects}}

\subsubsection{Encryption Suite}
Wrote various implementations of Encryption algorithms (RSA, DES) using GNU Multiprecision library.

\subsubsection{Kiosk ArcGIS}
 Created a Java Swing application that parsed XMLs to read paleontology data and display bone structures and 
 locations on a map with custom search and filters.

\subsubsection{Personal Shell}
Developed a shell for personal use in C. Implements pipes, redirection and signal processing.

\subsubsection{Dotfile Manager}
Wrote a manager for linux configuration files.
The manager ensures that the configurations are consistent and updated on all computers as well as tracks local changes.

\section{S{\color{gray}kills}}

\begin{multicols}{2}
	\begin{itemize}
	\item Proficient in C\#, C, C++, Bash, Python, \LaTeX
	\item Familiar golang, Rust, SQL, MongoDB, haskell, lisp and FORTRAN
	\item Linux and Unix based Operating Systems
	\item Agile Software Development
	\item Willingness to learn new techniques and technology
\end{itemize}
\end{multicols}

\section{A{\color{gray}ctivities}}

\begin{multicols}{2}
\begin{itemize}
	\item $3^{rd}$ place Microsoft campus coding competition
	\item 2 year Google Code Jam Qualifier
	\item Online coding challenges and ProjectEuler, codeforces, kattis
	\item Member ACM and Security Club
	\item Contributions to Open Source Projects
\begin{multicols}{2}
	\begin{itemize} 
		\item RITA 
		\item newsboat 
		\item qutebrowser 
		\item BroMongoDB 
	\end{itemize}
\end{multicols}
\end{itemize}
\end{multicols}

\end{document}
